Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-11 draft.tex
adding conclusions

%Given a full profile: use linear programming to maximize regret
%Given a partial profile: use techniques of Lu and Boutilier (2011).
\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the social choice rule is fixed beforehand; indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions. 
Moreover, it is usually assumed that the preferences of the voters are known completely.

%We argue that it is possible that the committee wants to precise some preferences about the aggregation.
In this draft we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
We note that previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
%We consider that the committee wants to express preferences for some voting rules
In this draft we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
\end{abstract}

\section{Introduction}

\begin{itemize}
\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}
\end{itemize}

@@

 In many real situations, however, it may be necessary to reason with partial preferences, as some prefer- ences are not available and too expensive to obtain (with respect to a cognitive or economic cost). 
This observation has motivated a number of recent works on

In this paper we relax the traditional assumptions.

%Robust decision criterion: minimax regret
We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.

%Incremental elicitation of preferences can help mitigating the cognitive and communication costs
We adopt an adaptive utility elicitation framrwork

@@

@@

@@

@@

\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight \\ information}
\label{sec:mmr}

%The regret-minimizing alternative may not be a possible winner for some voting rules.
The weights of a scoring rule can model different preferences of the committee. 
For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
However in general it can be difficult to set the weights in an appropriate way.

@@

@@

@@

%regret-based incremental elicitation method
\begin{itemize}
	\item Minimax regret can be used to guide the elicitation process
	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If we wish optimality, we can perform elicitation until minimax regret drops to zero.
	\item At each step, the system needs to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
	\item Type of questions that we can ask to the chair:
	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
\end{itemize}

Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
Indeed, it can be beneficial to interleave questions asked to the committee and questions asked to voters, depending on which is estimated to be more informative.

@@

@@

\section{Conclusions}  \label{sec:conclusions}
%  Possible future works: manipulation, 
We have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.
Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near optimal consensus choice in a limited number of steps.

Future works include considering the effect of strategic agents, and considering probabilistic methods.
% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
%{\small
\bibliography{biblio}
\bibliographystyle{plain} 
%}

>>>>

%Given a full profile: use linear programming to maximize regret
%Given a partial profile: use techniques of Lu and Boutilier (2011).
\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the voting rule is fixed beforehand, and the full preference information is provided by the voters.

As social choice moves to the web, the

the need for relaxing the assumptions

In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.

We then show how minimax regret can be used to drive the elicitation

We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.

%We consider that the committee wants to express preferences for some voting rules

\end{abstract}

\section{Introduction}
% indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions. 
%Moreover, it is usually assumed that the preferences of the voters are known completely.

@@

In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).

In this paper we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.

This observation has motivated a number of recent works on preference elicitation, including several works on social choice with partial profiles.

We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.

%We argue that it is possible that the committee wants to precise some preferences about the aggregation.s
% Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
%In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
%In this paper we relax the traditional assumptions.

%Incremental elicitation of preferences can help mitigating the cognitive and communication costs
%We adopt an adaptive utility elicitation framrwork

@@

Possible and necessary winner determination: in typical settings, there will be no necessary winner and too many possible winners.

While previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.

% We must engage in simultaneous elictation of the rule and of the preferences.

@@

\begin{itemize}
\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}.
Also this reference: \cite{Naamani-Dery2015}.
\end{itemize}

@@

% Theoretical complexity of partial completition

@@

\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight information}
\label{sec:mmr}

%Robust decision criterion: minimax regret
Minimax regret \cite{Savage1954} is a decision criterion that has been used for robust optimization under data uncertainty \cite{Kouvelis1997} and as well in decision-making with uncertain utility values  \cite{Salo2001,Boutilier2006}.

% we use max regret to measure the quality

% This leads to interesting tradeoffs in elicitation
%The regret-minimizing alternative may not be a possible winner for some voting rules.
% the value of certain preference information is often not worth the cost of obtaining it.
The weights of a scoring rule can model different preferences of the committee. 
For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).
However in general it can be difficult to set the weights in an appropriate way.

@@

Intuitively, the quality of a proposed alternative $a$ is how far from optimal $a$  could be in the worst case, given the current knowledge about the voting rule and about the voters' preferences.

@@

Notice that if $MMR(\pprofile, W)=0$, then $x^{*}(\pprofile,W)$  is a necessary co-winner.

@@

If the available information is too limited, the potential error associated with the robust winner (i.e., its max regret) may be unacceptable.

Minimax regret can be used to guide the elicitation process.
As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If we wish optimality, we can perform elicitation until minimax regret drops to zero.

At each step, the system needs to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule

In this Section, we describe different strategies to determine informative queries to ask next, with the goal of reducing $\MMR(\pprofile,W)$ quickly.

We propose an regret-based incremental elicitation method...

\paragraph{Strategies}

We develop some elicitation strategies for simultaneous elicitation of voters' preferences and of the scoring rule.
Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
Indeed, it can be beneficial to interleave questions asked to the committee and questions asked to voters, depending on which is estimated to be more informative.

@@

%Type of questions that we can ask to the chair:	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).

% we discuss the different forms of queries and develop several query strategies 
\paragraph{Query types}

@@

\section{Conclusions}  \label{sec:conclusions}
%  We have proposed the use of minimax regret as a means of robust winner determination to support the informational approximation of voting rules, as well as to guide the process of incremental elicitation of voter preferences.
%In this paper we have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.

In this paper we have considered a  social choice setting with partial  information about the voter's  
preferences and as well a partially specified voting rule.
We have proposed the use of minimax regret as a means of robust winner determination in this setting, and as well as to guide the process of incremental elicitation of voter preferences.
Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near-optimal consensus choice in a limited number of steps.
%Regret-based elicitation allows to determine near-optimal winners using only few information about the voters' preferences.
We mention some  important directions for future works.
First of all, further development of elicitation strategies, considering alternative heuristics, is an important direction. 
Second, we are interested in extending elicitation of voting rules going beyond scoring rules.
A third direction is that of considering probabilistic methods for elicitation.
Finally, we are interested in studying the effect of strategic agents, that may not report their true preferences.
% distribution-free heuristics

% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
%{\small
\bibliography{biblio}
\bibliographystyle{plain} 
%}
